\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-08-05 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
texte modèle encore

\begin{table}[htbp]
  \centering
  \caption{Calibration (2)}\label{tab:calib_TC}
\begin{center}
	\input{table_calibTC_combined.tex}
\end{center}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs. In columns (1), (3), (5) and (7) only ad-valorem costs are considered. In Columns (2), (4), (6) and (8), we model both ad-valorem and additive costs. $t$ is calibrated so that the ratio $t/\widetilde{p}_x$ from the model matches its empirical target, with $widetilde{p}^{\text{fas}}_x$ the average fas price set in place by those domestic firms that export. We theoretically define the export fas price through: $p_x = \tau p^{\text{fas}} +t$}}}
\end{table}

@@

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l|c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline
Fixed export cost: &  \multicolumn{2}{|c|}{Constant $f_x$} &  \multicolumn{2}{|c||}{Lower $f_x$} & \multicolumn{2}{|c|}{Constant $f_x$} & \multicolumn{2}{|c}{Lower $f_x$} \\ \hline
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\ \hline
%$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
%$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.4 &-3.4 &-3.4 &-3.4 &-6.4 &-6.4 &-6.4 &-6.4  \\
$\Delta \tau$ (in pp) & -3.4	&-1.4&	-3.40&	-1.40	&-6.4&	-3.1&	-6.4&	-3.1  \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-2.0&	0&	-3.3&	0&	-3.3  \\ \hline
$\Delta \mathcal{W}$ & 0.0202&	0.0295	&0.036&	0.053	&0.035&	0.052	&0.047&	0.064 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.232&	1.819&	2.207	&3.248	&2.179	&3.295&	2.872&	4.052   \\
\hline
\end{tabular}
\end{center}
{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs. The reduction in transport costs is expressed in percentage points. }}}
\end{table}

@@

In this first exercise, we contrast the effects of a reduction of international transport costs depending on whether this occurs through a reduction in ad-valorem costs only, or a combined reduction in both the additive and the multiplicative components. In Table \ref{tab:resultats_modele}, this relies on the results reported in Column (1) versus (2) for Air, Column (5) versus (6) for Vessel.\medskip

@@

Through which mechanism does it occur? As underlined by \cite{sorensen2014}, a reduction in the additive cost reduces the export-market price of the high-productivity exporters relative to the low-productive ones (this can be shown from Equation (\ref{eq:px})). Within the exporters category, this favors the more productive firms, whose market share, e.g. revenues increases relatively more, as can be shown from Equation (\ref{eq:rx}). Everything else equal, this pushes the average productivity on the export market upwards. In contrast to ad-valorem costs, the reduction in additive costs induces a \textit{within-exporters selection effect}, in favor of the more productive firms. At the general equilibrium, this within-exporters selection effect also affects the \textit{classic} selection effect at the extensive margin, at the heart of the \cite{melitz} model: As the expected export profit increases, it is necessary to be more productive to satisfy the free-entry condition: Everything else equal,

>>>>

\begin{table}[htbp]
  \centering
  \caption{Calibration (2)}\label{tab:calib_TC}
\begin{center}
	\input{table_calibTC_combined.tex}
\end{center}
{\parbox[l]{12cm}{ \vspace{4pt}\footnotesize{Notes: In Columns (1), (3), (5) and (7), we model oad-valorem costs only. In Columns (2), (4), (6) and (8), we model both ad-valorem and additive costs. $t$ is calibrated so that the ratio $t/\widetilde{p}_x$ from the model matches its empirical target, with $widetilde{p}^{\text{fas}}_x$ the average fas price set in place by those domestic firms that export. We theoretically define the export fas price through: $p_x = \tau p^{\text{fas}} +t$. TC = Transport Costs, expressed in percentage of the average fas export price.}}}
\end{table}

@@

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l||c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline  
$f_x$ final value &  \multicolumn{2}{|c|}{As in 1974} &  \multicolumn{2}{|c||}{Lower} & \multicolumn{2}{|c|}{As in 1974} & \multicolumn{2}{|c}{Lower } \\ \hline
& (A) & (B) & (C) & (D) & (E) & (F) &(G) & (H) \\ 
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline  
$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.4 &-3.4 &-3.4 &-3.4 &-6.4 &-6.4 &-6.4 &-6.4  \\
$\Delta \tau$ (in pp) & -3.4	&-1.4&	-3.40&	-1.40	&-6.4&	-3.1&	-6.4&	-3.1  \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-2.0&	0&	-3.3&	0&	-3.3  \\ \hline
$\Delta \mathcal{W}$ & 0.0202&	0.0295	&0.036&	0.053	&0.035&	0.052	&0.047&	0.064 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.232&	1.819&	2.207	&3.248	&2.179	&3.295&	2.872&	4.052   \\
\hline
\end{tabular}
\end{center}
{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs, expressed in percentage of the average export fas price. The reduction in transport costs is expressed in percentage points. }}}
\end{table}

@@

In this first exercise, we contrast the effects of a reduction of international transport costs depending on whether this occurs through a reduction in ad-valorem costs only, or a combined reduction in both the additive and the multiplicative components. In Table \ref{tab:resultats_modele}, this relies on the results reported in Column (A) versus (B) for Air, Column (E) versus (F) for Vessel.\medskip

@@

Through which mechanism does it occur? As underlined by \cite{sorensen2014}, a reduction in the additive cost reduces the export-market price of the high-productivity exporters relative to the low-productive ones (this can be shown from Equation (\ref{eq:px})). Within the exporters category, this favors the more productive firms, whose market share, e.g. revenues increases relatively more, as can be shown from Equation (\ref{eq:rx}). Everything else equal, this pushes the average productivity on the export market upwards.\footnote{This mechanism indirectly appears Figure \ref{fig:competitivity_air_decomp}, panel. Given our exercise that assumes a combined decrease in both the additive and the ad-valorem costs, at the general equilibrium, the threshold productivity on the export market $\widetilde{\varphi}^\ast_x$ still decreases, but to a lesser extent when the trade liberalization partly occurs through a reduction in additive costs. } In contrast to ad-valorem costs, the reduction in additive costs induces a \textit{within-exporters selection effect}, in favor of the more productive firms. At the general equilibrium, this within-exporters selection effect also affects the \textit{classic} selection effect at the extensive margin at the heart of the \cite{melitz} model: As the expected export profit increases, it is necessary to be more productive to satisfy the free-entry condition. Everything else equal, the threshold productivity on the domestic market increases, as well as the average productivity. Accordingly, the competitiveness effect increases by more when the trade liberalization involves a reduction in the additive component.

The more negative variety effect (Figure \ref{fig:welfare_decomp}) can be understood as a consequence of the above mechanism. Since the reduction in additive costs favors the more productive firms in terms of market share, entry on the export market is tougher leading to a lower mass of exporters (Figure \ref{fig:variety_air_decomp}). As the selection on the domestic market is also strengthened when trade liberalization involves a reduction in additive costs, the mass of active domestic firms reduces by a larger amount. From the consumer side, this induces a more negative variety effect that is welfare-detrimental everything else equal. As for the pure-iceberg case though, the strength of the competitiveness effect still dominates, inducing positive welfare gains, and even larger when the trade liberalization involves a reduction in additive costs.

\textbf{Faire l'exercice partant d'un monde avec les deux ad-valorem + iceberg, regarder ce qui se passe quand la baisse des coouts totaux est soit soit uniquement iceberg, soit uniquement ad-valorem? Plus proche de l'exercice de Sorensen. Plus clair sur les effets? }

\subsubsection{Reducing fixed export costs}

The above results underline the importance of the additive component of international trade costs. Trade liberalization still has positive welfare effects, and even larger when it relies on a reduction in additive costs. One might question the robustness of this last result to the type of trade liberalization considered. Indeed, the reduction in the fixed export costs seems empirically relevant to account for the larger share of exporting firms nowadays relative to the 1970s (Based on XXX, from 19\% in XXX to around 35\% in XXX). As underlined by \cite{melitz} \textbf{l'a-t-il MONTRE VRAIMENT ANALYTIQUEMENT? A VERIFIER}, the reduction of the fixed export cost is also welfare-enhancing, in presence of yet only ad-valorem variable trade costs. A natural question then emerges: To what extent is this result modified in presence of additive costs? Specifically, are the welfare gains of a fixed export costs decrease larger in presence of additive costs?

The answer can be found in Table \ref{tab:resultats_modele}, by comparing Columns (B) to (D) for Air, (F) to (H) for Vessel, the difference between these two columns (for each transport mode) being the lower value of the fixed export cost. Here again, the welfare gains of trade liberalization (under the form of a lower fixed export cost) are larger when variable trade costs involve a part of additive costs: If the effect are quantitatively modest in maritime transport (by 0.75 percentage points, from 3.3\% to 4.05\%), the decrease in the fixed export cost is more sizeable when variable costs are lower, as in air transport where the welfare gains almost double (from 1.82\% to 3.25\%).

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele_decompwelfare}
\begin{center}
\begin{tabular}{l||c|c|c|c||c|c|c|c}
\hline
Mode & \multicolumn{4}{|c||}{Air} & \multicolumn{4}{c}{Vessel} \\ \hline
$f_x$ final value &  \multicolumn{2}{|c|}{As in 1974} &  \multicolumn{2}{|c||}{Lower} & \multicolumn{2}{|c|}{As in 1974} & \multicolumn{2}{|c}{Lower } \\ \hline
& (A) & (B) & (C) & (D) & (E) & (F) &(G) & (H) \\
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$ & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline
%$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
%$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
%$\Delta TC$ (in pp) &-3.4 &-3.4 &-3.4 &-3.4 &-6.4 &-6.4 &-6.4 &-6.4  \\
%$\Delta \tau$ (in pp) & -3.4	&-1.4&	-3.40&	-1.40	&-6.4&	-3.1&	-6.4&	-3.1  \\
%$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-2.0&	0&	-3.3&	0&	-3.3  \\ \hline
%$\Delta \mathcal{W}$ & 0.0202&	0.0295	&0.036&	0.053	&0.035&	0.052	&0.047&	0.064 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.232&	1.819&	2.207	&3.248	&2.179	&3.295&	2.872&	4.052   \\ \hline
Variety effect (\%)&	-0.827	&0.747	&-2.670&	-1.132	&-1.323	&-0.126&	-3.061	& -1.857 \\
Price effect (\%)&	2.084&	1.455	&5.202&	4.444&	3.568	&3.001&	6.829&	6.059 \\ 
\hline
\end{tabular}
\end{center}
%{\parbox[l]{15cm}{ \vspace{4pt}\footnotesize{Notes: The reduction in transport costs is expressed in percentage points. }}}
\end{table}
